What would happen if we never knew about the normal distribution?

========================================================

This story is a very sad story about a world without a Normal distribution.  As statistician it is very difficult imagine a world without the Normal distribution.  She is the queen of the distributions is very elegant with a perfect symmetric shape and a lot of the other curves want to be  normal at the end. For some of the other curves it is very difficult because they have a lot of asymetry that it is difficult to change... 

Here is our queen…...

```{r fig.width=7, fig.height=6}
normal<-rnorm(10000)
library(ggplot2)
qplot(normal,geom='histogram')
```
How can happened that this blind world couldn’t  discover this magic curve?  We know that at the end all the problems when we have enough information we get a Normal distribution. But what happened if the Normal distribution does not exists? This means that with a huge sample size for some specific problem we will not get our precious Normal curve? Mmmm  difficult to believe …….


Could be the distruibution of 


In a parellel dimension, the normal distribution was never discovered.  Therefore there was no sampling theory.  If you were studying sizes of oranges, you had to measure the sizes of ALL of the oranges. You had no idea if the next sample would also be normally distributed.  

hmm restart. 

1) Normal Distribution exists but is not discovered.
- the normal distribution is using samples to summarize the entire population.  Most of the population is near an average.
- therefore without a normal or any "distribution," researchers would have to measure the entire population. They could not assume that the next sample would match the current sample.

2) Normal Distribution does not exist.
- the world revolves around a uniform, gamma, exponential distribution, other
- maybe it doesn't even have a distribution
- non normal distributions: uniform, gamma, exponential, cycling (sin/cos, tangent etc)
- music

World 2:
- 


Non-Normal Distributions:
Uniform
```{r fig.width=4, fig.height=3}
library(ggplot2)
x = c(rep (c(1:5),5))
qplot(x)
```

Bimodal
```{r fig.width=4, fig.height=3}
library(ggplot2)
x = rnorm(1000)
x1=x+5
x = c(x,x1)
qplot(x,)
```


You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(cars)
```

